---
title: "Qualify Media Runs for Instruments"
author: "Seahorse Bioscience"
output: html_document
---
##### Date: `r as.Date(Sys.time())`
##### Instrument:  `r A<-readxl::read_excel('FILE')[,1:2];A[which(A[,1]=="Instrument Serial"),2]`
##### Filename: `r basename('FILE')`
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r,warning=FALSE,message=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
x<-'FILE' #FilePath
XL.Level<-readxl::read_excel(x,sheet=PipeFish::fndLVLs(x)) %>% rename(.,O2=`O2 (mmHg)`)
XL.Rate<-readxl::read_excel(x,sheet='Rate')
grp<-XL.Level %>% 
  mutate(absO2=abs(152-O2)) %>%
  mutate(abspH=abs(pH-7.4)) %>%
  group_by(Well) %>%
  summarize(xpH=max(abspH),xO2=max(absO2))
```

#### Level Plots


```{r}
library(ggplot2)
library(ggthemes)
XLev<-XL.Level %>% dplyr::select(.,Tick,O2,pH,Well)
ggplot(XLev,aes(Tick,O2,Well)) +geom_line(aes(col=Well))+theme_bw()+ggtitle("O2 Levels")
ggplot(XLev,aes(Tick,pH,Well)) +geom_line(aes(col=Well))+theme_bw()+ggtitle("pH Levels")

```




 

#### Outliers +/- 10 from 152 mmHg O2, spec < 3

```{r}
spec1<-grp %>% filter(xO2 >10) %>% nrow()
```
 n = `r spec1`,  `r c("Fail","Pass")[(spec1<3)+1]`

#### Outliers +/- 20 from 152 mmHg O2, spec < 1

```{r}
spec2<-grp %>% filter(xO2 >20) %>% nrow()
```
   
n = `r spec2`,  `r c("Fail","Pass")[(spec2<1)+1]`

   
#### Outliers +/- 0.1 from 7.4 pH, spec < 1

```{r}
spec3 <-grp %>% filter(.,xpH >0.1) %>% nrow(.)
```
n = `r spec3`, `r c("Fail","Pass")[(spec3<1)+1]`

#### pH rates are 0.0 +/- 10 mpH/minute

```{r}
spec4<-XL.Rate %>% 
  mutate(abspR=abs(ECAR)) %>%
  group_by(Well) %>%
  summarize(W=max(abspR)) %>%
  filter(.,W > 10) %>%
  nrow(.)
```

n = `r spec4`, `r c("Fail","Pass")[(spec4<1)+1]`


